### 2020-08-28 thesis/chap_1.tex
remove surperfulus roc curves

The reported adjusted  $R^{2}$ for our urbanization and agricultural expansion random forest models are $0.57$ and $0.56$ respectively. The values for AUC are comparatively higher: varying between $0.841$ and $0.931$ (depending on the validation set) for Agricultural Expansion and between $0.921$ and $0.939$ for Urbanization (see summary table \ref{tab:R_squares_AUC} and see figures \ref{fig:roc_agex} and \ref{fig:roc_urb} for the spatial validation ROC curves). The resampled AUC (10-folds CCV) is equally as high with means of $0.929 \pm .002$ and $0.938 \pm 0.002$ respectively (see figure \ref{fig:roc_rs} for the 10-fold ROC curves).\\

>>>>

The reported adjusted  $R^{2}$ for our urbanization and agricultural expansion random forest models are $0.57$ and $0.56$ respectively. The values for AUC are comparatively higher: varying between $0.841$ and $0.931$ (depending on the validation set) for Agricultural Expansion and between $0.921$ and $0.939$ for Urbanization (see summary table \ref{tab:R_squares_AUC}). The resampled AUC (10-folds CCV) is equally as high with means of $0.929 \pm .002$ and $0.938 \pm 0.002$ respectively (see figure \ref{fig:roc_rs} for the 10-fold ROC curves).\\
